### 2025-08-02 multiple-regression.qmd
20250802 - fix implemented for calculation of target share
https://github.com/nflverse/nflfastR/pull/505/commits/2308d30cd96d10ffdd6966a1eccb1f7c4750be47

Let's say we want to use a number of variables to predict a wide receiver's fantasy performance.
We want to consider several [predictors](#sec-correlationalStudy), including the player's age, height, weight, and target share.
We have only a few [predictors](#sec-correlationalStudy) and our sample size is large enough such that [overfitting](#sec-overfitting) is not likely a concern.

On a weekly basis, target share is computed as the number of targets a player receives divided by the team's total number of targets.
It would be nice to compute it this way for seasonal data, as well; however, for calculating seasonal target share, the `nflfastR` [@R-nflfastR] package currently sums up the player's weekly target share.
Thus, seasonal target share (unlike weekly target share)—as it is currently calculated—does not range from 0–1.
For example, if a player has a weekly target share of 15%, that would be a seasonal (cross-week-summed) target share of 2.55 ($0.15 \times 17 \; \text{games} = 2.55$).

@@

We could also generate the model-implied prediction of fantasy points for any value of the [predictor variables](#sec-correlationalStudy).
For instance, here are the number of fantasy points expected for a Wide Receiver who is 23 years old, is 6'2" tall (72 inches), weighs 200 pounds, and has a (cross-week-summed) target share of 3 (which reflects an approximate target share of 17.6% percent per game; i.e., $0.176 = \frac{3}{17 \; \text{games}}$):

```{r}
predict(
  quadraticTermsRegressionModel,
  newdata = data.frame(
    age = 23,
    height = 72,
    weight = 200,
    target_share = 3
  )
)
```

@@

predictedValue <- predict(
  quadraticTermsRegressionModel,
  newdata = data.frame(
    age = 23,
    height = 72,
    weight = 200,
    target_share = 3
  )
)
```

@@

```{r}
age <- 23
height <- 72
weight <- 200
target_share <- 3

>>>>

Let's say we want to use a number of variables to predict a wide receiver's fantasy performance.
We want to consider several [predictors](#sec-correlationalStudy), including the player's age, height, weight, and target share.
Target share is computed as the number of targets a player receives divided by the team's total number of targets.
We have only a few [predictors](#sec-correlationalStudy) and our sample size is large enough such that [overfitting](#sec-overfitting) is not likely a concern.

@@

We could also generate the model-implied prediction of fantasy points for any value of the [predictor variables](#sec-correlationalStudy).
For instance, here are the number of fantasy points expected for a Wide Receiver who is 23 years old, is 6'2" tall (72 inches), weighs 200 pounds, and has a target share of 50% (i.e., 0.5):

```{r}
predict(
  quadraticTermsRegressionModel,
  newdata = data.frame(
    age = 23,
    height = 72,
    weight = 200,
    target_share = .5
  )
)
```

@@

predictedValue <- predict(
  quadraticTermsRegressionModel,
  newdata = data.frame(
    age = 23,
    height = 72,
    weight = 200,
    target_share = .5
  )
)
```

@@

```{r}
age <- 23
height <- 72
weight <- 200
target_share <- .5
